\textbf{NBA Party}

### 2017-07-03 cardinal_analytx_presentation/nightlife_and_sports.tex
Added citations to intro. Added plot showing it\'s a coin toss whether we win as a function of the odds.

\begin{frame}   \frametitle{What is the problem?}
  \begin{block}{Do pro athletes party to the detriment of their performance?}
    It's not unreasonable to think that what happens off the court affects outcome, but!
    \begin{itemize}       \item Can we even measure this?
      \item Are there systematic tendencies?     \end{itemize}
  \end{block} \end{frame}

\begin{frame}   
  \frametitle{Who cares?}
  \begin{block}{\$400 billion spent on sports betting per year in the US.\footnote{NBA Commissioner Adam Silver}}

@@

    Knowing the causal relation between partying and next-day performance might inform
    \begin{itemize}       \item How coaches set team-rules, 
      \item How travel schedules are determined.     \end{itemize}
  \end{block}
\end{frame}

@@

  Further, it's not obvious that we will find an effect. \end{frame}

@@

    A team is expected to meet the spread $\frac{1}{2}$ the time.   \end{block} \end{frame}

>>>>

\begin{frame}   \frametitle{What is the problem?}
  \begin{block}{Do pro athletes party to the detriment of their performance?}
    Anecdotally, yes.\footnote{Cestone ('17), Price ('15), Concepcion ('15), Miller ('15), Campbell ('15).}

    It's not unreasonable to think that what happens off the court affects outcome, but!
    \begin{itemize}       \item Can we even measure this?
      \item Are there systematic tendencies?     \end{itemize}
  \end{block} \end{frame}

\begin{frame}   
  \frametitle{Who cares?}
  \begin{block}{\$400 billion spent on sports betting per year in the US.\footnote{NBA Commissioner Adam Silver, 2014.}}

@@

    Knowing the causal relation between partying and next-day performance might inform
    \begin{itemize}       
      \item How coaches set team-rules, 
      \item How travel schedules are determined.
      \item Which players to bench, and when.
      \end{itemize}
  \end{block}
\end{frame}

@@

  Further, it's not obvious that we will find an effect.

  \begin{block}{Previous research}
    Players under-perform proportion of shots made on Sundays.\footnote{Chase ('15): 1,092 NBA players under-perform relative to their own season-long average out of 2,035 who took at least one shot on Sunday.}

    Teams under-perform bookmakers expectations on Sunday afternoons when on the road.\footnote{Ezekowitz, ('14): Only 129 out of 284 games did the away team meet the spread, using 2008-14 data.}   \end{block}

\end{frame}

@@

    A team is expected to meet the spread $\frac{1}{2}$ the time.\footnote{Dubner and Levitt, 2006}
  \end{block}
  \begin{block}{Bookmaker money-lines}     The odds that a team will beat their opponent.

    After conditioning on odds, successful prediction is like a coin-flip.   \end{block} \end{frame}
